Can historical data predict population responses to climate change experiments?

### 2016-12-18 precip/manuscript/precip_ms.tex
a few revisions to methods

In the climate model, the $\chi$ and $\xi$ terms are replaced with, 
\begin{equation}
\boldsymbol{C}\xi_{j}^S 
\label{eqn:survC}
\end{equation}
where $\xi$ gives a vector of coefficients describing the effects of a set of soil moisture covariates $\boldsymbol{C}$ in treatment $h$ and year $t$ on the survival rate of species $j$. $\boldsymbol{C}$ is a vector of seasonal average soil moisture at a set of species-specific seasons and time lags and can include interaction effects between plant size, $u$ and the soil moisture covariates.  These interaction effects allow the effect of soil moisture to vary with plant size.

@@

After fitting the random year effects (null) and climate models to the observational data, we generated predictions from these models for each of the vital rates in the experimental plots. We then assessed performance of the climate and null models by calculating the mean square error between the predictions and observations for each of the vital rates. In addition we evaluated whether the climate model predicted treatment effects of similar direction and magnitude to those observed in the experiment.  We did this by extracting the soil moisture coefficients contained in $\xi$ for each of the vital rates and then multiplying those by the appropriate soil moisture covariates for each year and treatment level in the experiment.  The average of this product across all the years of the experiment then gives the predicted treatment coefficient for treatment level $h$. These predicted treatment effects can then be compared directly to the treatment effects fitted in the treatment model in the term $\chi$.

@@

We evaluated cover predictions from the climate and year effects model similarly.  We first fit the

@@

The experimental drought shelter successfully reduced the soil moisture in the study plots in the spring and summer, while irrigation successfully increased soil moisture \ref{fig:spotm}. Our continuous data

>>>>

In the climate model, the $\chi$ and $\xi$ terms are replaced with, 
\begin{equation}
\boldsymbol{C}\xi_{j}^S 
\label{eqn:survC}
\end{equation}
where $\xi$ gives a vector of coefficients describing the effects of a set of soil moisture covariates $\boldsymbol{C}$ in treatment $h$ and year $t$ on the survival rate of species $j$. $\boldsymbol{C}$ is a vector of seasonal average soil moisture and can include interaction effects between plant size, $u$, and the soil moisture covariates that allow the effects of soil moisture to vary with plant size.

@@

After fitting the random year effects (null model) and climate models to the observational data, we generated predictions from these models for each of the vital rates in the experimental plots. We then assessed performance of the climate and null models by calculating the mean square error between the predictions and observations for each of the vital rates. In addition we evaluated whether the climate model predicted treatment effects of similar direction and magnitude to those observed in the experiment.  We did this by extracting the soil moisture coefficients contained in $\xi$ for each of the vital rates and then multiplying those by the appropriate soil moisture covariates for each year and treatment level in the experiment. We then averaged these products across the years in the experiment to get the effects of the experiment predicted by the soil moisture model. These predicted treatment effects can then be compared directly to the treatment parameters in the term $\chi$.

@@

@@

The experimental drought shelter successfully reduced the soil moisture in the study plots in the spring and summer, while irrigation successfully increased soil moisture \ref{fig:spotm}. Our seasonal model of soil moisture in the experiment indicated that
